---
title: "Appendix 1: Performance Maps"
author: "Odd Jacobson"
date: "2023-01-26"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This document plots the HR estimates of all the emulated sampling regimes over the data from the complete segments.

The plots show the 95% UD estimates with 95% CIs using the data from the different sampling regimes. 
Each plot shows the total locations from the complete, but the green points are the ones that were selected in the regimes, and the pink points are the data that were thinned out.

Load packages 
```{r, message=FALSE, warning=FALSE}
library(tidyverse)
library(ctmm)
library(sf)
library(lubridate)
library(janitor)
library(ggmap)
```

### AA Group

Get boundaries and points and change to sf object
```{r}
## change to sf objects

# data
aa_data_sf <- readRDS("Intermediate/DATA_aa.rds") %>% 
  purrr::map(ctmm::as.sf) %>% 
  reduce(rbind) %>% 
  mutate(id = gsub("R", "S", identity),
         id = ifelse(id == "C1", "C30", 
                     ifelse(id == "C2", "C20",
                            ifelse(id == "C3", "C10",
                                   ifelse(id == "C4", "C6",
                                          ifelse(id == "C5", "C3",
                                                 ifelse(id == "S1", "S30",
                                                        ifelse(id == "S2", "S20",
                                                               ifelse(id == "S3", "S10",
                                                                      ifelse(id == "S4", "S6",
                                                                             ifelse(id == "S5", "S3", id)))))))))),
         id = factor(id, levels = c("C30", "C20", "C10","C6", "C3", "S30", "S20", "S10", "S6", "S3"))) %>%
  dplyr::select(id, geometry) %>% 
  filter(!id == "all") %>% 
  st_transform("+proj=utm +zone=16 +north +datum=WGS84 +units=km +no_defs +ellps=WGS84 +towgs84=0,0,0")

# HR mean boundary
aa_akde_sf <- readRDS("Intermediate/AKDE_aa.rds") %>% 
  purrr::map(ctmm::as.sf, level.UD = 0.95) %>% 
  reduce(rbind) %>% 
  mutate(name = gsub("R", "S", name),
         id = gsub( " .*$", "", name ), # get id by subsetting everything before space in name
         id = ifelse(id == "C1", "C30", 
                     ifelse(id == "C2", "C20",
                            ifelse(id == "C3", "C10",
                                   ifelse(id == "C4", "C6",
                                          ifelse(id == "C5", "C3",
                                                 ifelse(id == "S1", "S30",
                                                        ifelse(id == "S2", "S20",
                                                               ifelse(id == "S3", "S10",
                                                                      ifelse(id == "S4", "S6",
                                                                             ifelse(id == "S5", "S3", id)))))))))),
         id = factor(id, levels = c("C30", "C20", "C10","C6", "C3", "S30", "S20", "S10", "S6", "S3"))) %>%
  filter(str_detect(row.names(.), "est"),
         !id == "all") %>%
  dplyr::select(id, geometry) %>% 
  st_transform("+proj=utm +zone=16 +north +datum=WGS84 +units=km +no_defs +ellps=WGS84 +towgs84=0,0,0")

# HR confidence boundaries
aa_akde_CI <- readRDS("Intermediate/AKDE_aa.rds") %>% 
  purrr::map(ctmm::as.sf, level.UD = 0.95) %>% 
  reduce(rbind) %>% 
  mutate(name = gsub("R", "S", name),
         id = gsub( " .*$", "", name ),
         id = ifelse(id == "C1", "C30", 
                     ifelse(id == "C2", "C20",
                            ifelse(id == "C3", "C10",
                                   ifelse(id == "C4", "C6",
                                          ifelse(id == "C5", "C3",
                                                 ifelse(id == "S1", "S30",
                                                        ifelse(id == "S2", "S20",
                                                               ifelse(id == "S3", "S10",
                                                                      ifelse(id == "S4", "S6",
                                                                             ifelse(id == "S5", "S3", id)))))))))),
         id = factor(id, levels = c("C30", "C20", "C10","C6", "C3", "S30", "S20", "S10", "S6", "S3"))) %>%
  filter(!str_detect(row.names(.), "est"),
         !id == "all") %>%
  dplyr::select(id, geometry) %>% 
  st_transform("+proj=utm +zone=16 +north +datum=WGS84 +units=km +no_defs +ellps=WGS84 +towgs84=0,0,0")

# get all points
ce_all_data <- readRDS("Intermediate/DATA_aa.rds") %>% 
  purrr::map(ctmm::as.sf) %>% 
  reduce(rbind) %>% 
  mutate(id = gsub("R", "S", identity)) %>% 
  dplyr::select(id, geometry) %>% 
  filter(id == "all")  %>% 
  dplyr::select(-id) %>% 
  st_transform("+proj=utm +zone=16 +north +datum=WGS84 +units=km +no_defs +ellps=WGS84 +towgs84=0,0,0")
```

Get data that was removed from complete segments to create regimes. These points will be shown on the maps.

```{r}

## getting all thinned data
# get unique ids
ids <- unique(aa_data_sf$id)

# make list
aa_data_list <- aa_data_sf %>% 
  as.data.frame() %>% 
  group_split(id)

# change names of list
names(aa_data_list) <- ids

# make empty list to be filled
aa_thinned_data <- list()

# run loop over to get data that was thinned from each regime
for (i in ids){
  aa_thinned_data[[i]] <- anti_join(as.data.frame(aa_all_data), aa_data_list[[i]], by = "geometry")
}

# bind into data frame and make sf object
aa_thinned_data <- as.data.frame(do.call(rbind, aa_thinned_data)) %>%
  rownames_to_column("id") %>% 
  mutate(id = sub("\\..*", "", id)) %>% 
  st_as_sf(crs = "+proj=utm +zone=16 +north +datum=WGS84 +units=km +no_defs +ellps=WGS84 +towgs84=0,0,0")

```

Plot

```{r}

# get colors
colors <- c("missing points" = "#de4968", "used points" = "#40bd72")
shape <- c("missing points" = 1, "used points" = 16)
size <- c("missing points" = 0.8, "used points" = 1.2)
labels <- c("missing points", "used points")

# plot
p1 <- ggplot() +
  geom_sf(data = aa_data_sf, 
          aes(color = "used points", shape = "used points", size = "used points"),
          inherit.aes = FALSE, alpha = 0.9) +
  geom_sf(data = aa_thinned_data, 
          aes(color = "missing points", shape = "missing points", size = "missing points"),
          inherit.aes = FALSE, alpha = 1) +
  geom_sf(data = aa_akde_CI, 
          inherit.aes = FALSE, 
          fill = NA, linetype = "dashed", alpha = 0.3, size = 0.3) +
  geom_sf(data = aa_akde_sf,
          inherit.aes = FALSE, 
          fill =NA , alpha = 0.06, size = 0.8) +
  ggspatial::annotation_scale(location = "bl", 
                              width_hint = 0.3,
                              height = unit(4,'pt'),
                              style = 'ticks') +
  coord_sf(datum = st_crs("+proj=utm +zone=16 +north +datum=WGS84 +units=km +no_defs +ellps=WGS84 +towgs84=0,0,0"), 
           xlim=c(676.500,680.000), ylim=c(1161.000, 1164.000)) +
  scale_color_manual(values = colors, labels = labels, name = "") +
  scale_shape_manual(values = shape, labels = labels, name = "") +
  scale_size_manual(values = size, labels = labels, name = "") +
  scale_x_continuous(labels = scales::label_number(accuracy = .1)) +
  scale_y_continuous(labels = scales::label_number(accuracy = .1, big.mark = "")) +
  guides(color=guide_legend(override.aes=list(size = 8)))+
  labs( x = "Easting (km)", y = "Northing (km)") +
  theme_bw(base_family = "ArcherPro Book") +
  theme(legend.position="bottom", 
        legend.title = element_blank(),
        legend.text=element_text(size=14),
        #axis.text.x = element_text(angle=45, hjust = 1),
        axis.title = element_blank(),
        axis.text = element_blank(),
        axis.ticks = element_blank(),
        strip.text = element_text(size = 15)) +
  facet_wrap(~factor(id, levels = c("C30", "C20", "C10","C6", "C3", "S30", "S20", "S10", "S6", "S3")), nrow = 2) 
```

```{r, include=FALSE}
# Save plot
file.name.performance <- paste0("AA_performance_plots_",
                                format(Sys.time(), "%Y_%m_%d_%H%M%S"), ".jpg")

ggsave(here::here("Figures", file.name.performance),
       plot = p1,
       width = 3400,
       height = 2000,
       units = "px")
```

## CE Group

Get boundaries and points and change to sf object
```{r}
## change to sf objects

# data
ce_data_sf <- readRDS("Intermediate/DATA_ce.rds") %>% 
  purrr::map(ctmm::as.sf) %>% 
  reduce(rbind) %>% 
  mutate(id = gsub("R", "S", identity),
         id = ifelse(id == "C1", "C30", 
                     ifelse(id == "C2", "C20",
                            ifelse(id == "C3", "C10",
                                   ifelse(id == "C4", "C6",
                                          ifelse(id == "C5", "C3",
                                                 ifelse(id == "S1", "S30",
                                                        ifelse(id == "S2", "S20",
                                                               ifelse(id == "S3", "S10",
                                                                      ifelse(id == "S4", "S6",
                                                                             ifelse(id == "S5", "S3", id)))))))))),
         id = factor(id, levels = c("C30", "C20", "C10","C6", "C3", "S30", "S20", "S10", "S6", "S3"))) %>%
  dplyr::select(id, geometry) %>% 
  filter(!id == "all") %>% 
  st_transform("+proj=utm +zone=16 +north +datum=WGS84 +units=km +no_defs +ellps=WGS84 +towgs84=0,0,0")

# HR mean boundary
ce_akde_sf <- readRDS("Intermediate/AKDE_ce.rds") %>% 
  purrr::map(ctmm::as.sf, level.UD = 0.95) %>% 
  reduce(rbind) %>% 
  mutate(name = gsub("R", "S", name),
         id = gsub( " .*$", "", name ), # get id by subsetting everything before space in name
         id = ifelse(id == "C1", "C30", 
                     ifelse(id == "C2", "C20",
                            ifelse(id == "C3", "C10",
                                   ifelse(id == "C4", "C6",
                                          ifelse(id == "C5", "C3",
                                                 ifelse(id == "S1", "S30",
                                                        ifelse(id == "S2", "S20",
                                                               ifelse(id == "S3", "S10",
                                                                      ifelse(id == "S4", "S6",
                                                                             ifelse(id == "S5", "S3", id)))))))))),
         id = factor(id, levels = c("C30", "C20", "C10","C6", "C3", "S30", "S20", "S10", "S6", "S3"))) %>%
  filter(str_detect(row.names(.), "est"),
         !id == "all") %>%
  dplyr::select(id, geometry) %>% 
  st_transform("+proj=utm +zone=16 +north +datum=WGS84 +units=km +no_defs +ellps=WGS84 +towgs84=0,0,0")

# HR confidence boundaries
ce_akde_CI <- readRDS("Intermediate/AKDE_ce.rds") %>% 
  purrr::map(ctmm::as.sf, level.UD = 0.95) %>% 
  reduce(rbind) %>% 
  mutate(name = gsub("R", "S", name),
         id = gsub( " .*$", "", name ),
         id = ifelse(id == "C1", "C30", 
                     ifelse(id == "C2", "C20",
                            ifelse(id == "C3", "C10",
                                   ifelse(id == "C4", "C6",
                                          ifelse(id == "C5", "C3",
                                                 ifelse(id == "S1", "S30",
                                                        ifelse(id == "S2", "S20",
                                                               ifelse(id == "S3", "S10",
                                                                      ifelse(id == "S4", "S6",
                                                                             ifelse(id == "S5", "S3", id)))))))))),
         id = factor(id, levels = c("C30", "C20", "C10","C6", "C3", "S30", "S20", "S10", "S6", "S3"))) %>% 
  filter(!str_detect(row.names(.), "est"),
         !id == "all") %>%
  dplyr::select(id, geometry) %>% 
  st_transform("+proj=utm +zone=16 +north +datum=WGS84 +units=km +no_defs +ellps=WGS84 +towgs84=0,0,0")

# get all points
ce_all_data <- readRDS("Intermediate/DATA_ce.rds") %>% 
  purrr::map(ctmm::as.sf) %>% 
  reduce(rbind) %>% 
  mutate(id = gsub("R", "S", identity)) %>% 
  dplyr::select(id, geometry) %>% 
  filter(id == "all")  %>% 
  dplyr::select(-id) %>% 
  st_transform("+proj=utm +zone=16 +north +datum=WGS84 +units=km +no_defs +ellps=WGS84 +towgs84=0,0,0")
```

Get data that was removed from complete segments to create regimes. These points will be shown on the maps.

```{r}

## getting all thinned data
# get unique ids
ids <- unique(ce_data_sf$id)

# make list
ce_data_list <- ce_data_sf %>% 
  #as.data.frame() %>% 
  group_split(id)

# change names of list
names(ce_data_list) <- ids

# make empty list to be filled
ce_thinned_data <- list()

# run loop over to get data that was thinned from each regime
for (i in ids){
  ce_thinned_data[[i]] <- anti_join(as.data.frame(ce_all_data), ce_data_list[[i]], by = "geometry")
}

# bind into data frame and make sf object
ce_thinned_data <- as.data.frame(do.call(rbind, ce_thinned_data)) %>%
  rownames_to_column("id") %>% 
  mutate(id = sub("\\..*", "", id)) %>% 
  st_as_sf(crs = "+proj=utm +zone=16 +north +datum=WGS84 +units=km +no_defs +ellps=WGS84 +towgs84=0,0,0")

```

Plot

```{r}

# plot
p3 <- ggplot() +
  geom_sf(data = ce_data_sf, 
          aes(color = "used points", shape = "used points", size = "used points"),
          inherit.aes = FALSE, alpha = 0.9) +
  geom_sf(data = ce_thinned_data, 
          aes(color = "missing points", shape = "missing points", size = "missing points"),
          inherit.aes = FALSE, alpha = 1) +
  geom_sf(data = ce_akde_CI, 
          inherit.aes = FALSE, 
          fill = NA, linetype = "dashed", alpha = 0.3, size = 0.3) +
  geom_sf(data = ce_akde_sf,
          inherit.aes = FALSE, 
          fill =NA , alpha = 0.06, size = 0.8) +
  ggspatial::annotation_scale(location = "bl", 
                              width_hint = 0.3,
                              height = unit(4,'pt'),
                              style = 'ticks') +
  coord_sf(datum = st_crs("+proj=utm +zone=16 +north +datum=WGS84 +units=km +no_defs +ellps=WGS84 +towgs84=0,0,0"), 
           xlim=c(675.700,677.500), ylim=c(1162.000, 1164.100)) +
  scale_color_manual(values = colors, labels = labels, name = "") +
  scale_shape_manual(values = shape, labels = labels, name = "") +
  scale_size_manual(values = size, labels = labels, name = "") +
  scale_x_continuous(labels = scales::label_number(accuracy = .1)) +
  scale_y_continuous(labels = scales::label_number(accuracy = .1, big.mark = "")) +
  guides(color=guide_legend(override.aes=list(size = 8)))+
  labs( x = "Easting (km)", y = "Northing (km)") +
  theme_bw(base_family = "ArcherPro Book") +
  theme(legend.position="bottom", 
        legend.title = element_blank(),
        legend.text=element_text(size=14),
        #axis.text.x = element_text(angle=45, hjust = 1),
        axis.title = element_blank(),
        axis.text = element_blank(),
        axis.ticks = element_blank(),
        strip.text = element_text(size = 15)) +
  facet_wrap(~factor(id), nrow = 2) 
```

```{r, include=FALSE}
# Save plot
file.name.performance <- paste0("CE_performance_plots_",
                                format(Sys.time(), "%Y_%m_%d_%H%M%S"), ".jpg")

ggsave(here::here("Figures", file.name.performance),
       plot = p3,
       width = 3400,
       height = 2000,
       units = "px")
```


